A boundary-integral framework to simulate \\ viscous erosion of a porous medium

### 2018-04-17 docs/methods/erosion_methods.tex
final edits and submitted to JCP and arxiv

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{\bf Acknowledgments} We would like to thank Manas Rachh for supplying the FMM for the Stokes double-layer potential.

@@

\bibitem[Cao et~al.(2010)Cao, Gunzburger, Hua, Wang, et~al.]{cao2010coupled}
Yanzhao Cao, Max Gunzburger, Fei Hua, Xiaoming Wang, et~al.
\newblock Coupled stokes-darcy model with beavers-joseph interface boundary
  condition.
\newblock \emph{Communications in Mathematical Sciences}, 8\penalty0
  (1):\penalty0 1--25, 2010.

@@

\bibitem[Power and Miranda(1987)]{pow-mir1987}
H.~Power and G.~Miranda.
\newblock Second kind integral equation formulation of stokes' flows past a
  particle of arbitrary shape.
\newblock \emph{SIAM Journal on Applied Mathematics}, 47\penalty0 (4):\penalty0
  689--698, 1987.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{\bf Acknowledgments} We would like to thank Manas Rachh for
supplying the FMM for the Stokes double-layer potential. BQ and NM were
supported by Florida State University startup funds and Simons
Foundation Mathematics and Physical Sciences-Collaboration Grants for
Mathematicians.

@@

\bibitem[Cao et~al.(2010)Cao, Gunzburger, Hua, Wang, et~al.]{cao2010coupled}
Yanzhao Cao, Max Gunzburger, Fei Hua, Xiaoming Wang, et~al.
\newblock Coupled Stokes-Darcy model with Beavers-Joseph interface boundary
  condition.
\newblock \emph{Communications in Mathematical Sciences}, 8\penalty0
  (1):\penalty0 1--25, 2010.

@@

\bibitem[Power and Miranda(1987)]{pow-mir1987}
H.~Power and G.~Miranda.
\newblock Second kind integral equation formulation of Stokes' flows past a
  particle of arbitrary shape.
\newblock \emph{SIAM Journal on Applied Mathematics}, 47\penalty0 (4):\penalty0
  689--698, 1987.
